PHAT RAID, yo

### 2014-05-13 paper/paper.tex
Add a system organization section

\usepackage{tikz}
\usetikzlibrary{graphdrawing}

@@

\newcommand{\chubby}[0]{\textsc{Chubby}}
\newcommand{\phat}[0]{\textsc{Phat}}
\newcommand{\phatraid}[0]{\textsc{PhatRaid}}
\newcommand{\raid}[1]{\textsc{RAID #1}}
\newcommand{\paxos}[0]{\textsc{Paxos}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

@@

We implemented Viewstamped Replication\cite{liskov2012viewstamped} to achieve
consensus in the file system. Listing \ref{lst:genfsm} defines how to handle
prepare messages sent to a node in the replica state. It is piecewise defined by
pattern matching on the arguments. The first two definition clauses use the
\lstinline!when! keyword to specify arbitrary, required relationships between
the matched variables.

>>>>

\usepackage{tikz}
\usetikzlibrary{backgrounds}
\usetikzlibrary{fit}
\usetikzlibrary{positioning}

\pgfdeclarelayer{b}
\pgfdeclarelayer{f}
\pgfsetlayers{b,main,f}

\newcommand{\plate}[4]{
\begin{pgfonlayer}{b}
\node (invis#1) [draw, color=white, inner sep=1pt,rectangle,fit=#2] {};
\end{pgfonlayer}
\begin{pgfonlayer}{f}
\node (capt#1) [ below left=0 pt of invis#1.south east, xshift=2pt,yshift=1pt, fill=black!15]
{\footnotesize{#3}};
\end{pgfonlayer}
\begin{pgfonlayer}{b}
\node (#1) [fill=black!15, rounded corners, inner sep=5pt, rectangle,fit=(invis#1) (capt#1),#4] {};
\end{pgfonlayer}
}

@@

\newcommand{\chubby}[0]{\textsc{Chubby}}
\newcommand{\phat}[0]{\textsc{Phat}}
\newcommand{\phatraid}[0]{\textsc{PhatRaid}}
\newcommand{\raid}[1]{\textsc{RAID #1}}
\newcommand{\paxos}[0]{\textsc{Paxos}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
  \begin{tikzpicture}
    [->,scale=.8,]
    \node [rectangle, draw, thick] (raidclient) at (0,2) {Raid Client};
    \node [rectangle, draw, thick] (client1) at (-4,1) {Client 1};
    \node [rectangle, draw, thick] (client2) at (0,0) {Client 2};
    \node [rectangle, draw, thick] (client3) at (4,1) {Client 3};
    \node [rectangle, draw, thick] (vr11) at (-7, -2) {Master};
    \node [rectangle, draw, thick] (vr12) at (-5, -2) {Replica};
    \node [rectangle, draw, thick] (vr13) at (-3, -2) {Replica};
    \node [rectangle, draw, thick] (vr21) at (-2, -4) {Master};
    \node [rectangle, draw, thick] (vr22) at (0, -4) {Replica};
    \node [rectangle, draw, thick] (vr23) at (2, -4) {Replica};
    \node [rectangle, draw, thick] (vr31) at (3, -2) {Master};
    \node [rectangle, draw, thick] (vr32) at (5, -2) {Replica};
    \node [rectangle, draw, thick] (vr33) at (7, -2) {Replica};

    \foreach \to in {client1, client2, client3}
    \draw [thick] (raidclient) -- (\to);
    \foreach \to in {vr11, vr12, vr13}
    \draw [thick] (client1) -- (\to);
    \foreach \to in {vr21, vr22, vr23}
    \draw [thick] (client2) -- (\to);
    \foreach \to in {vr31, vr32, vr33}
    \draw [thick] (client3) -- (\to);

    \plate{clientnode}{(raidclient)(client1)(client2)(client3)}{Client Node}{}
    \plate{pc1}{(vr11)(vr12)(vr13)}{Phat Cluster \#1}{}
    \plate{pc2}{(vr21)(vr22)(vr23)}{Phat Cluster \#2}{}
    \plate{pc3}{(vr31)(vr32)(vr33)}{Phat Cluster \#3}{}

  \end{tikzpicture}
  \caption{Organizational Diagram}
  \label{fig:organization}
\end{figure}

@@

Figure \ref{fig:organization} depicts the organization of our system. The
raid-client delegates communication to each client. Each client is connected to
one \phat{} cluster, which has a master and a number of replicas.

Each \phat{} cluster maintains a file system which is separate and distinct from
the file systems of other \phat{} clusters. Generally, two phat clusters do not
communicate.

\subsection{Implenting RAID on \phat{}}

@@

We implemented Viewstamped Replication\cite{liskov2012viewstamped} to achieve
consensus in the file system. Listing \ref{lst:genfsm} defines how to handle
prepare messages sent to a node in the replica state. It is piecewise defined by
pattern matching on the arguments. The first two definition clauses use the
\lstinline!when! keyword to specify arbitrary required relationships between the
matched variables.
